Supporting Information

### 2018-04-17 SupportingInformation.Rmd
Cause4copula plots are made

<!--Shya to implement the modelling we discussed on 2018 04 12 and make results appear here!-->
```{r cause4copula, echo=F, cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"))}
source("Cause4copula.R")
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF.pdf", width=12, height=6)
op<-par(mfrow=c(2,4),mar=c(3,3.5,3,3.5), mgp=c(1.5,0.5,0))

Plotter_Cause4copula_GOF(fcode=3,method = "spearman")
Plotter_Cause4copula_GOF(fcode=13,method="spearman")
Plotter_Cause4copula_GOF(fcode=4,method = "spearman")
Plotter_Cause4copula_GOF(fcode=14,method="spearman")

Plotter_Cause4copula_GOF(fcode=3,method = "kendall")
Plotter_Cause4copula_GOF(fcode=13,method="kendall")
Plotter_Cause4copula_GOF(fcode=4,method = "kendall")
Plotter_Cause4copula_GOF(fcode=14,method="kendall")

@@

#-------------------------------------------------------------
#pdf("./Results/Cause4copula_results/Clayton_spearman.pdf")
#Plotter_Cause4copula_stat(numsim=500,fcode=3,method="spearman",lb=0,ub=0.1)
#dev.off()

#pdf("./Results/Cause4copula_results/Clayton_kendall.pdf")
#Plotter_Cause4copula_stat(numsim=500,fcode=3,method="spearman",lb=0,ub=0.1)
#dev.off()

#pdf("./Results/Cause4copula_results/Gumbel_spearman.pdf")
#Plotter_Cause4copula_stat(numsim=500,fcode=4,method="spearman",lb=0,ub=0.1)
#dev.off()

#pdf("./Results/Cause4copula_results/Gumbel_kendall.pdf")
#Plotter_Cause4copula_stat(numsim=500,fcode=4,method="kendall",lb=0,ub=0.1)
#dev.off()

#pdf("./Results/Cause4copula_results/SClayton_spearman.pdf")
#Plotter_Cause4copula_stat(numsim=500,fcode=13,method="spearman",lb=0,ub=0.1)
#dev.off()

#pdf("./Results/Cause4copula_results/SClayton_kendall.pdf")
#Plotter_Cause4copula_stat(numsim=500,fcode=13,method="kendall",lb=0,ub=0.1)
#dev.off()

#pdf("./Results/Cause4copula_results/SGumbel_spearman.pdf")
#Plotter_Cause4copula_stat(numsim=500,fcode=14,method="spearman",lb=0,ub=0.1)
#dev.off()

#pdf("./Results/Cause4copula_results/SGumbel_kendall.pdf")
#Plotter_Cause4copula_stat(numsim=500,fcode=14,method="kendall",lb=0,ub=0.1)
#dev.off()
```

>>>>

<!--Shya to implement the modelling we discussed on 2018 04 12 and make results appear here!-->
```{r cause4copula, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"))}
source("Cause4copula.R")
set.seed(seed=101)
#---------------------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF.pdf", width=12, height=6)
op<-par(mfrow=c(2,4),mar=c(3,3.5,3,3.5), mgp=c(1.5,0.5,0))

Plotter_Cause4copula_GOF(fcode=3,method = "spearman",num_keep_last=500,BS=100)
Plotter_Cause4copula_GOF(fcode=13,method="spearman",num_keep_last=500,BS=100)
Plotter_Cause4copula_GOF(fcode=4,method = "spearman",num_keep_last=500,BS=100)
Plotter_Cause4copula_GOF(fcode=14,method="spearman",num_keep_last=500,BS=100)

Plotter_Cause4copula_GOF(fcode=3,method = "kendall",num_keep_last=500,BS=100)
Plotter_Cause4copula_GOF(fcode=13,method="kendall",num_keep_last=500,BS=100)
Plotter_Cause4copula_GOF(fcode=4,method = "kendall",num_keep_last=500,BS=100)
Plotter_Cause4copula_GOF(fcode=14,method="kendall",num_keep_last=500,BS=100)

@@

#-------------------------------------------------------------
pdf("./Results/Cause4copula_results/Clayton_spearman.pdf")
Plotter_Cause4copula_stat(numsim=50,fcode=3,method="spearman",lb=0,ub=0.1)
dev.off()

pdf("./Results/Cause4copula_results/Clayton_kendall.pdf")
Plotter_Cause4copula_stat(numsim=50,fcode=3,method="spearman",lb=0,ub=0.1)
dev.off()

pdf("./Results/Cause4copula_results/Gumbel_spearman.pdf")
Plotter_Cause4copula_stat(numsim=50,fcode=4,method="spearman",lb=0,ub=0.1)
dev.off()

pdf("./Results/Cause4copula_results/Gumbel_kendall.pdf")
Plotter_Cause4copula_stat(numsim=50,fcode=4,method="kendall",lb=0,ub=0.1)
dev.off()

pdf("./Results/Cause4copula_results/SClayton_spearman.pdf")
Plotter_Cause4copula_stat(numsim=50,fcode=13,method="spearman",lb=0,ub=0.1)
dev.off()

pdf("./Results/Cause4copula_results/SClayton_kendall.pdf")
Plotter_Cause4copula_stat(numsim=50,fcode=13,method="kendall",lb=0,ub=0.1)
dev.off()

pdf("./Results/Cause4copula_results/SGumbel_spearman.pdf")
Plotter_Cause4copula_stat(numsim=50,fcode=14,method="spearman",lb=0,ub=0.1)
dev.off()

pdf("./Results/Cause4copula_results/SGumbel_kendall.pdf")
Plotter_Cause4copula_stat(numsim=50,fcode=14,method="kendall",lb=0,ub=0.1)
dev.off()
```
